Concurrent Programming with CXL

### 2020-06-18 book/paper.tex
Latest

@@

Some programming languages favor a completely different way of implementing
synchronization using so-called \emph{actors}~\cite{HBS73}.  Actors are
processes that have only private memory and communicate through messages.
Given that there is no shared memory in the actor model, there is no need
for critical sections.  Instead, some sequential process owns a particular
piece of data and other processes access it by sending request messages
to the process and optionally waiting for response messages.  Each process
handles one message at a time, serializing all access to the data it owns.

@@

Figure~\ref{fig:actor} shows a solution to the producer/consumer problem using
an actor.  \texttt{pc\_actor} is essentially a matchmaker: it matches
\texttt{.produce} requests with \texttt{.consume} requests.
Sometimes it may have buffered \texttt{.consume} requests and is waiting for
\texttt{.produce} requests, and sometimes it is vice versa.
The variable \texttt{balance} specifies what the situation is: if it is positive
then it has buffered \texttt{.produce} requests;
if it is negative
then it has buffered \texttt{.consume} requests.
Note that both \texttt{balance} and \texttt{requests} are variables that are
local to the \texttt{pc\_actor} process.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=4in]{figures/actor-crop.pdf}
\end{center}
\caption{Depiction of three actors.  The producer does not receive messages.}
\label{fig:actorpic}
\end{figure}

@@

Some programming languages favor a completely different way of implementing
synchronization using so-called \emph{actors}~\cite{HBS73}.  Actors are
processes that have only private memory and communicate through message queues.
See Figure~\ref{fig:actorpic} for an illustration.
Given that there is no shared memory in the actor model (other than the message
queues, which have built-in synchronization), there is no need
for critical sections.  Instead, some sequential process owns a particular
piece of data and other processes access it by sending request messages
to the process and optionally waiting for response messages.  Each process
handles one message at a time, serializing all access to the data it owns.

@@

Figure~\ref{fig:actor} shows a CXL solution to the producer/consumer problem using
an actor (as illustrated in Figure~\ref{fig:actorpic}.
\texttt{pc\_actor} is essentially a matchmaker: it matches
\texttt{.produce} requests with \texttt{.consume} requests.
Sometimes it may have buffered \texttt{.consume} requests and is waiting for
\texttt{.produce} requests, and sometimes it is vice versa.
The variable \texttt{balance} specifies what the situation is: if it is positive
then it has buffered \texttt{.produce} requests;
if it is negative
then it has buffered \texttt{.consume} requests.
Note that both \texttt{balance} and \texttt{requests} are variables that are
local to the \texttt{pc\_actor} process.
